A Hitchhiker's Guide to Reproducible Research in R

### 2021-06-15 manuscript.Rmd
explain how reproduction works with repro

These information make internal dependencies to other files in the project and external dependencies to R packages explicit.
`repro` can use these information to infer a Makefile for the dependencies on other files and a Dockerfile that includes all required packages.
In day-to-day work the simplest solution is to use the function `repro::automate()` which both infers a Makefile and a Dockerfile from all RMarkdown files (all files with the ending `.Rmd`).
Everytime you changed the `repro`-metadata, change the output format, or add a new RMarkdown, the Makefile and Dockerfile are potentially outdated and you should run `repro::automate()` to keep them up to date.
The function `repro::automate()` does not overwrite manual changes and there is no harm in running it too often.

>>>>

This information makes internal dependencies to other files in the project and external dependencies to R packages explicit.
`repro` can use this information to infer a Makefile for the dependencies on other files and a Dockerfile that includes all required packages.
In day-to-day work the simplest solution is to use the function `repro::automate()` which both infers a Makefile and a Dockerfile from all RMarkdown  (all files with the ending `.Rmd`) and there respective repro metadata.
Every time you change the `repro`-metadata, change the output format, or add a new RMarkdown, the Makefile and Dockerfile are potentially outdated, and you should run `repro::automate()` to keep them up to date.
The function `repro::automate()` does not overwrite manual changes, and there is no harm in running it too often.
Besides, the Makefile and the Dockerfile repro generates a few more files in the `.repro` directory (which we will explain in detail later), all of which you should add and commit to Git.

When you or people who received your project from GitHub want to reproduce the project, they can ask repro to explain how this should be done:

```{r}
repro::rerun()
```

However, users do not have to have repro installed, in fact, they do not even need R installed. 
The two Make commands `make docker` and `make -B DOCKER=TRUE` together with an installation of Make and Docker are sufficient.
They can be pasted into a terminal and will reproduce the project in many cases.
Some projects, however, are not as easy to make reproducible.
As explained above, repro is merely a simplified interface.
These simplifications are possible because of two restrictions.
First, the project can only rely on R packages for the Dockerfile and second, it can have no multilayered preprocessing for the Makefile.
Lifting these restrictions requires the user to interact more directly with Make or Docker.
Hence, it is necessary to understand what these commands do to satisfy more complicated requirements because then you need to understand how repro structures its interaction with Make and Docker.

Let us dissect the command for reproducing a repro project: `make docker && make -B DOCKER=TRUE`.
The command `make docker` will trigger Make to build the target `docker`.
The recipe for this target builds an image from your Dockerfile.
The `&&` combines two commands in one line.
The call `make` without any explicit target will build the Make target `all`, where the flag `-B` means that Make will consider all prerequisites as outdated and hence will rebuild everything.
repro constructs Make targets so that if you supply `DOCKER=TRUE` they are executed within the Docker image of the project.
